---
output: github_document
---


```{r, include = FALSE, message=F, warning=F}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CoronaExtra

The goal of CoronaExtra is to provide some geological and historical data regarding the spread of COVID-19 throughout the world

## Installation

You can install the released version of CoronaExtra from github with:

``` {r inc, eval = FALSE, message=F, warning=F}
install_github("HappySpectre/CoronaExtra")
```

## Example

The following coed shows how to use the C19WorldMap and COVID19vsTime functions.

```{r example1, message=F, warning=F}
library(CoronaExtra)
C19WorldMap(type = 1, date = "8/5/20")
```


```{r example2, message=F, warning=F}
library(CoronaExtra)
COVID19vsTime(Country = "Iran", Start = "2020-08-01", Stop = "2020-10-02")
```


```{r deathsimport, echo=F, message=F, warning=F}
library(readr)
url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"
  death <- read_csv(url)
```
The data set used in this package as reference is provided by Johns Hopkins University and can be found at https://github.com/CSSEGISandData/COVID-19.

```{r data, message=F, warning=F, echo=F}
data <- head(as.data.frame(death[,2:8]))
```


```{r deaths, message=F, warning=F}
head(data)
```

